%-------------------------
% Academic CV in the style of resume/raw/cv_merged.tex
% Compile with XeLaTeX.
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{array}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{fontspec}
\usepackage{xeCJK}

%----------FONT OPTIONS----------
\IfFontExistsTF{TeX Gyre Termes}{\setmainfont{TeX Gyre Termes}}{\setmainfont{Times New Roman}}

% Chinese font preference requested for this CV.
\IfFontExistsTF{Source Han Serif SC}{%
  \setCJKmainfont{Source Han Serif SC}
  \IfFontExistsTF{Source Han Serif CN}{%
    \setCJKfallbackfamilyfont{\CJKrmdefault}{Source Han Serif CN}
  }{}%
}{%
  \IfFontExistsTF{Source Han Serif CN}{%
    \setCJKmainfont{Source Han Serif CN}
  }{%
    \IfFontExistsTF{Songti SC}{%
      \setCJKmainfont{Songti SC}
    }{%
      \IfFontExistsTF{Noto Serif CJK SC}{%
        \setCJKmainfont{Noto Serif CJK SC}
      }{}%
    }%
  }%
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{4.5pt}

% Adjust margins to match the source template.
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\raggedright\large
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands from the source template
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeScholarship}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\texturl}[2]{\href{#1}{\textcolor{blue}{#2}}}
\definecolor{mygray}{gray}{0.96}
\newcommand{\TLDR}[1]{{\footnotesize \colorbox{mygray}{#1}}}
\newcommand{\faFilePdfO}{\faFilePdf}
\newcommand{\faExternalLinkIcon}{\faIcon{external-link-alt}}

\definecolor{pubred}{RGB}{210,80,80}
\newcommand{\pub}[1]{\textbf{\textcolor{pubred}{#1}}}

\newcommand{\me}{\textbf{\underline{Bo Yang}}}
\newcommand{\meCo}{\textbf{\underline{Bo Yang*}}}
\newcommand{\chinesename}{{\fontsize{18}{22}\selectfont 「杨博」}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\LARGE \MakeUppercase{Bo Yang}\chinesename} \vspace{4pt} \\ \vspace{4pt}
    \small
    \href{mailto:byangbf@connect.ust.hk}{\raisebox{-0.2\height}\faEnvelope\ \underline{byangbf@connect.ust.hk}}
    \hspace{8pt}
    \href{https://borisyang326.github.io/}{\raisebox{-0.2\height}\faHome\ \underline{https://borisyang326.github.io/}}
    \hspace{8pt}
    \href{https://github.com/BorisYang326}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/BorisYang326}}
    \\ \vspace{2pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Hong Kong University of Science and Technology}{Hong Kong, China}
      {\textit{Ph.D. Student in Arts and Machine Creativity}}{\textit{Jan. 2026 -- Present}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         Co-supervised by Prof. \textit{\texturl{https://whluo.github.io/}{Wenhan Luo}} and Prof. \textit{\texturl{https://hongbofu.people.ust.hk/}{Hongbo Fu}}
         }}
     \end{itemize}
     \vspace{-0.5em}

    \resumeSubheading
      {ShanghaiTech University}{Shanghai, China}
      {\textit{Master of Science in Computer Science}}{\textit{Sept. 2022 -- Aug. 2025}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         Advisor: Prof. \textit{\texturl{https://www.ying-cao.com/}{Ying Cao}}, \textbf{GPA}: 3.82/4.0
         }}
     \end{itemize}
     \vspace{-0.5em}

    \resumeSubheading
      {University of California, Berkeley}{Berkeley, California, US}
      {\textit{ShanghaiTech-UC Berkeley Summer School Exchange Program}}{\textit{Jul. 2019 -- Aug. 2019}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{GPA}: 4.0/4.0
         }}
     \end{itemize}
     \vspace{-0.5em}

    \resumeSubheading
      {ShanghaiTech University}{Shanghai, China}
      {\textit{Bachelor of Science in Computer Science}}{\textit{Sept. 2018 -- Jun. 2022}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
         \textbf{GPA}: 3.32/4.0
         }}
     \end{itemize}
  \resumeSubHeadingListEnd


%-----------RESEARCH INTEREST-----------
\section{Research Interest}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    Creative Content (Image / Graphic Design) Generation, Unified Multimodal Models, Visual CoT
    }}
\end{itemize}


%-----------PUBLICATIONS-----------
\section{Publications}
\begin{enumerate}[leftmargin=0.35in, label={[\arabic*].}]
    \item{
     \textbf{Beyond VLM-Based Rewards: Diffusion-Native Latent Reward Modeling}
     \quad{\href{https://arxiv.org/abs/2602.11146}{\faFilePdfO}}
     \quad{\href{https://github.com/HKUST-C4G/diffusion-rm}{\faGithub}}
     \\
     Gongye Liu, \me, Yida Zhi, Zhizhou Zhong, Lei Ke, Didan Deng, Han Gao, Yongxiang Huang, Kaihao Zhang, Hongbo Fu, Wenhan Luo \\
     \textit{Accepted by \pub{ICML 2026}} \\
     \TLDR{Diffusion-native reward modeling for image generation evaluation.}
     }

    \item{
     \textbf{Harnessing Layered Graphic Designs with Real Intentions for Text-to-Design Generation}
     \quad{\href{https://songxyjoy.github.io/LADEREIN/}{\faExternalLinkIcon}}
     \\
     Xinya Song, \me, Ying Cao \\
     \textit{Accepted by \pub{CVPR 2026 (findings track)}} \\
     \TLDR{Layered design benchmark with real complex intentions, learned alignment metric, and diffusion baseline for text-to-design.}
     }

     \item{
     \textbf{Order Matters: Learning Element Ordering for Graphic Design Generation}
     \quad{\href{https://borisyang326.github.io/ordermatters.html}{\faExternalLinkIcon}}
     \quad{\href{https://dl.acm.org/doi/10.1145/3730858}{\faFilePdfO}}
     \quad{\href{https://github.com/BorisYang326/OrderGOL}{\faGithub}}
     \\
     \me, Ying Cao\\
     \textit{Accepted by \pub{ACM Transactions on Graphics (SIGGRAPH 2025)}} \\
     \TLDR{An unsupervised content-adaptive neural ordering framework learns better element sequences for graphic design generation.}
     }
\end{enumerate}


%-----------RESEARCH PROJECTS-----------
\section{Research Projects}
\begin{enumerate}[leftmargin=0.35in, label={[\arabic*].}]
    \item{
     \textbf{CoRT: Latent Reflective Chain-of-Thought for Text-to-Image Generation} \\
     \textbf{[Co-first author]}, In Progress \\
     \TLDR{Text-to-image generation via latent multi-turn self-reflection in unified generation-understanding models.}
     }

    \item{
     \textbf{Learning Cross-Modal Interaction for Joint Image-Layout Template Generation} \\
     \textbf{[Second author]}, ECCV 2026 (Under Review) \\
     \TLDR{Joint image-layout diffusion with learned backbone communication for faster, more faithful design template generation.}
     }
\end{enumerate}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://c4g-hkust.github.io/}{C4 Group}, HKUST}{Hong Kong, China}
      {\textit{Research Assistant, supervised by Prof. \texturl{https://whluo.github.io/}{Wenhan Luo}}}{\textit{Aug. 2025 -- Jan. 2026}}
      \resumeItemListStart
        \resumeItem{Worked on projects about visual latent CoT and multi-modal generation.}
      \resumeItemListEnd

    \resumeSubheading
      {Shanghai BnZ Animation Studio}{Shanghai, China}
      {\textit{Co-founder}}{\textit{Sept. 2022 -- Jan. 2025}}
      \resumeItemListStart
        \resumeItem{Founded a studio dedicated to scientific visualization through graphic design, animations, and videos.}
        \resumeItem{Designed over 50 animations and videos for research entities such as \texturl{https://www.microsate.com/}{IAMCAS} and \texturl{https://pubs.acs.org/journal/amrcda}{the Journal of AMR}.}
      \resumeItemListEnd

    \resumeSubheading
      {VRVC-Lab, ShanghaiTech University}{Shanghai, China}
      {\textit{Research Intern, supervised by Prof. \texturl{http://www.yu-jingyi.com/}{Jingyi Yu} and Prof. \texturl{https://www.xu-lan.com/}{Lan Xu}}}{\textit{Jan. 2022 -- Sept. 2022}}
      \resumeItemListStart
        \resumeItem{Contributed to two papers for SIGGRAPH 2022 and SIGGRAPH Asia 2022, designing paper figures and producing demonstration videos.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------AWARDS-----------
\section{Awards}
\begin{itemize}[leftmargin=0.15in, label={}]
    \resumeScholarship{\textit{\textbf{Excellent Graduate}}, ShanghaiTech University}{\textit{Aug. 2025}}
    \resumeScholarship{\textit{\textbf{Outstanding Teaching Assistant}} in SIST, ShanghaiTech University}{\textit{Nov. 2023 / Nov. 2024}}
    \resumeScholarship{\textit{\textbf{Merit Student}} of ShanghaiTech University (\textbf{top 10\%})}{\textit{Dec. 2023}}
    \resumeScholarship{\textit{\textbf{Overseas Exchange Scholarship}}, ShanghaiTech University}{\textit{May 2019}}
\end{itemize}


%-------------------------------------------
\end{document}
